### 2023-03-12 main/chapter_searches.tex
explain ntuple

% posterior
Perhaps we now wanted to see where in the overflow bin this event landed, and
compare the signal and background distributions there.
That would be inspection of the \textbf{posterior}
\begin{equation}
p(x) = \prob{x}{d, h} = \frac{L(x)}{Z}\pi(x),
\end{equation}
which is a prior probability distribution specialized by the data;
it simply uses the likelihood to filter simulated samples
(like `skimming an ntuple'),
then re-normalizes them to a probability distribution within the constraint.

>>>>

% posterior
Perhaps we now wanted to see where in the overflow bin this event landed, and
compare the signal and background distributions there.
That would be inspection of the \textbf{posterior}
\begin{equation}
p(x) = \prob{x}{d, h} = \frac{L(x)}{Z}\pi(x),
\end{equation}
which is a prior probability distribution specialized by the data;
it simply uses the likelihood to filter simulated samples
(like `skimming an ntuple'%
\footnote{%
This is a reference to colloquial particle physics jargon;
an `ntuple' is a ROOT TTree, which is a generic data structure peculiar to the
ROOT software framework~\cite{ROOT}.
A TTree resembles a columnar collection of named arrays and jagged arrays,
and is entirely unlike the `tree' structures of mathematics, computer
science, or dendrology.
}),
then re-normalizes them to a probability distribution within the constraint.
